\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue]{classic}                  % optional argument are 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.87]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% Hyperlinks
\usepackage{hyperref}								% to use hyperlinks
\definecolor{linkcolour}{rgb}{0,0.2,0.6}			% hyperlinks setup
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

% personal data
\firstname{Connor}
\familyname{J. McCann}
%\title{Resumé title (optional)}               % optional, remove the line if not wanted
\address{1555 N Columbus Ave}{Glendale, CA 91202}    % optional, remove the line if not wanted
%\mobile{+30 698 4385057}                    % optional, remove the line if not wanted
\phone{(818) 321-8280}                      % optional, remove the line if not wanted
%\fax{fax (optional)}                          % optional, remove the line if not wanted
\email{connor.j.mccann@gmail.com}                      % optional, remove the line if not wanted
%\email{\href{mailto:s.dakourou@gmail.com}{s.dakourou@gmail.com}}                      % optional, remove the line if not wanted
\homepage{github.com/cjmccann}
%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[64pt][0.4pt]{picture}                         % '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Some quote (optional)}                 % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\vspace*{-2\baselineskip}
\maketitle
\vspace{-1.5\baselineskip}

\section{Education}
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}
\cventry{May 2014}{Tufts University}{Medford, MA}{}{}{
    \begin{itemize} 
        \item Bachelor of Arts, Clinical Psychology
        \item Minor in Computer Science
        \item GPA 3.89/4.00, \textit{Summa Cum Laude}
    \end{itemize} 
}

\section{Experience}
%\cventry{June 2014 - Present}{Software Development Engineer, Test}{Pegasystems}{Cambridge MA}{}{}{\hspace{3 mm}$\bullet$ Research, pilot, and implement a UI Testing} %Framework using Ruby, RSpec, and WebDriver.} %\newline{} $\bullet$ Faciliate daily operations and stability of framework, coordinate new tests from teams in US, India, and Poland.}
%\cventry{June 2014 - Present}{Software Development Engineer, Test}{Pegasystems}{Cambridge MA}{}{\hspace{3 mm}$\bullet$ Research, pilot, and implement an automated UI Testing Framework with Ruby, RSpec, and Selenium WebDriver }
\cventry{Mar 2017 - Present}{Software Engineer III}{Pegasystems}{Cambridge, MA}{}{
    \begin{itemize} 
        \item Expand engine to identify minimal needed subset of JavaScript and CSS based on component usage.
        \item Improve application load-time and performance by excluding unused static content.
        \item Design and create reports to analyze optimized JavaScript and CSS inclusion.
    \end{itemize} 
}
\cventry{Mar 2016 - Mar 2017}{Software Engineer II}{Pegasystems}{Cambridge, MA}{}{
    \begin{itemize} 
        \item Designed and executed conversion of product-wide UI to React.
        \item Enhanced internal tooling by building Eclipse plugin to version control foundational product records.
    \end{itemize} 
}
\cventry{June 2014 - Mar 2016}{Software Engineer}{Pegasystems}{Cambridge, MA}{}{
    \begin{itemize} 
        \item Researched, designed, and implemented cross-platform automated UI testing framework with Ruby, RSpec, Selenium WebDriver, and Appium.
        \item Coordinated testing effort between 25 teams in the US, India, and Poland, including travel to Hyderabad and Kraków offices.
    \end{itemize} 
}
\cventry{Sept 2013 - May 2014}{Research Intern}{Massachusetts General Hospital-Harvard Center}{Boston, MA}{}{
    \begin{itemize}
        \item Aided research operations through data entry, patient scheduling, and office management.
    \end{itemize}        
}
\cventry{May 2012 - Aug 2012}{Research Volunteer}{Schizophrenia Aftercare Research, UCLA}{Los Angeles, CA}{}{
    \begin{itemize}
        \item Acted as peer mentor for patients participating in cognitive remediation research project.
    \end{itemize}
}

\section{Personal Projects}
\cventry{Sep 2017}{Trade First Aid}{tradefirstaid.rotoballer.com}{Ruby on Rails}{\scriptsize In collaboration with Rotoballer.com}{
    \begin{itemize}
        \item Built and maintained fantasy football trade tool to provide analysis customized to league and settings.
        \item Implemented functionality to sync Yahoo accounts and teams, keeping league rosters updated.
        \item Since Sep 2017, over 22,000 teams and 2,000 leagues imported from Yahoo accounts.
    \end{itemize}
}
\cventry{Mar 2017}{Baseball-On-Draft}{baseball-on-draft.herokuapp.com}{Ruby on Rails}{}{
    \begin{itemize}
        \item Built fantasy baseball draft aid to aggregate and weight Steamer, ZiPS, and PECOTA projections.
        \item Based on projections and league settings, provide player-value analysis and real-time draft feedback.
    \end{itemize}
}

\section{Community Service}
\cventry{Sept 2011 - Jan 2014}{Philanthropy Chair}{Sigma Phi Epsilon, Mass Zeta Chapter}{Tufts University}{}{
    \begin{itemize}
        \item Arranged chapter participation in Boston Walk to Defeat ALS, Relay for Life, and projects in local Somerville community.
    \end{itemize}
}
\cventry{Oct 2011 - May 2013}{Committee Member}{Relay for Life, American Cancer Society}{Tufts University}{}{
    \begin{itemize}
        \item Helped recruit teams and members to raise money for the event.
    \end{itemize}
}

\section{Languages, Tools, and Technologies}
\cvline{Proficient}{\textbf{JavaScript}, \textbf{Ruby}, Rails, RSpec, Selenium WebDriver, Spanish}
\cvline{Intermediate}{\textbf{Java}, React, HTML5, CSS3, Test Driven Development}
\cvline{Basic}{\textbf{TypeScript}, \textbf{Python}, \textbf{C++}, Polymer, Node.js }
\end{document}
